\bf Appendix: Stop Lying to Me: New Visual Tools to Choose the Most Honest Nonlinear Dimension Reduction

### 2025-06-26 appendix.qmd
Added parameter choices

For illustration purposes, we only selected cells generated with inDrops ($n=5858$ cells) and UMAP and tSNE cell embeddings. Also, @xia2023 used first $9$ principal components to generate the UMAP and tSNE. The objective is to assess the optimized layout by scDEED, and if it does not accurately represent the three clusters with small separations of the PBMC dataset, then select a reasonable \gD{} layout.

>>>>

For illustration purposes, we only selected cells generated with inDrops ($n=5858$ cells). Also, @xia2023 used first $9$ principal components to generate the UMAP and tSNE with default hyper-parameters. The objective is to assess the optimized layout by scDEED, and if it does not accurately represent the three clusters with small separations of the PBMC dataset, then select a reasonable \gD{} layout.

### 2025-06-26 appendix.tex
Added parameter choices

For illustration purposes, we only selected cells generated with inDrops
(\(n=5858\) cells) and UMAP and tSNE cell embeddings. Also,
\citet{xia2023} used first \(9\) principal components to generate the
UMAP and tSNE. The objective is to assess the optimized layout by
scDEED, and if it does not accurately represent the three clusters with
small separations of the PBMC dataset, then select a reasonable \gD{}
layout.

>>>>

For illustration purposes, we only selected cells generated with inDrops
(\(n=5858\) cells). Also, \citet{xia2023} used first \(9\) principal
components to generate the UMAP and tSNE with default hyper-parameters.
The objective is to assess the optimized layout by scDEED, and if it
does not accurately represent the three clusters with small separations
of the PBMC dataset, then select a reasonable \gD{} layout.
